### 2010-03-26 docs/architecture/architecture.tex
some more reorgaization and more on the 'standard' test problems

@@

\item {\tt planar\_heat} \\[-3mm]

@@

@@

\item {\tt test\_spherical} \\[-3mm]
\end{itemize}

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  Each problem
will have one or more inputs files (for example, {\tt test2/inputs\_2d}
which override the default values for one or more runtime parameters.
The code is run simply as:
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d
\end{verbatim}

@@

>>>>

\subsection{`Standard' Test Problems}

@@

@@

Spherical heat maps a spherical star (a Chandrasekhar-mass white dwarf)
onto the Cartesian domain and uses an external heat source to cause
the star to expand.  This is the 3-d analogue of the {\tt test\_basestate}
unit test.  This problem was discussed in \cite{multilevel}.

@@

{\tt test\_convect} drives convection through a plane-parallel
atmosphere using an externally-specified heat source.  This problem
was used to compare with compressible solvers in \cite{lowMach3}
and to test the multilevel algorithm in \cite{multilevel}.

\item {\tt test\_spherical} \\[-3mm]

{\tt test\_spherical} sets up an isentropically stratified star
and stirs it up with a random velocity field.  The low Mach number
constraint is replaced with the anelastic constraint (through
the {\tt beta\_type} runtime parameter).  Analytically, under
these conditions, the density of the star should not change.
This test problem was discussed in \cite{wdconvect}.

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  Each problem
will have one or more inputs files (for example, {\tt test2/inputs\_2d}
which override the default values for one or more runtime parameters.
The code is run simply as:
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d
\end{verbatim}
As the code runs, it will output both plotfiles and checkpoint files.
By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoint files are named {\tt chk}{\em
  nnnnn}.

To restart a calculation from a checkpoint file, either edit the inputs
file, setting
\begin{verbatim}
  restart = n
\end{verbatim}
where {\tt n} is the step number of the checkpoint file to restart
from.  Equivalently, you can override the value in the inputs file
by adding {\tt --restart n} to the commandline, as 
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d --restart n
\end{verbatim}

@@

\subsection{Defining Runtime Parameters}
